### 2013-02-12 doc/xps2013/proposal.tex
more work on intro, research and work plan

While some irregular applications can be restructured to better exploit locality, aggregating requests to increase message size, and manage the additional challenges of load balance and synchronization across multinode systems, the work to do so is formidable and requires knowledge and skills pertaining to distributed systems far beyond those of most application programmers.

@@

\being{itemize}
\item \textbf{TBD}
\end{itemize}

@@

Grappa (Figure~\ref{fig:grappa}) has three main software components: \begin{description}

@@

\comment{Luis, don't rant.    -mark
Luis: Ehm, gup you! It wasnt a rant, we are not even sure what our model is and this will take work... and before we know it, we cant cleanly do optimization. As you wish, leave it out, the current state is pretty sloppy... so if we get a comment on this, you will buy beers.

@@

>>>>

%% I don't think we need the parahraph below. 
% While some irregular applications can be restructured to better exploit
% locality, aggregating requests to increase message size, and manage the
% additional challenges of load balance and synchronization across multinode
% systems, the work to do so is formidable and requires knowledge and skills
% pertaining to distributed systems far beyond those of most application
% programmers.

@@

\begin{itemize}
\item \textbf What is the right system architecture support for irregular applications, including architecture, communication and storage?
\item \textbf What are the necessary language and compiler support for large-scale, data-intensive irregular applications?
\item \textbf How do we comprehensively evaluate performance of graph analytics systems?
\end{itemize}

@@

The current Grappa prototype (Figure~\ref{fig:grappa}) has three main software components: \begin{description}

@@

\comment{Luis, don't rant.    -mark
Luis: Ehm, it wasnt a rant, we are not even sure what our model is and this will take work... and before we know it, we cant cleanly do optimization. As you wish, leave it out, the current state is pretty sloppy... so if we get a comment on this, you will buy beers.

@@

\section{Work Plan}
\label{sec:plan}

Our research plan can be divided horizontally into three core areas:
programming languages/compilers; communication and storage; and benchmarking. Below we outline how we
plan to advance these fronts over the next four years.

\vspace{2ex}

%% TODO: need to expand below.

\noindent\textbf{Year 1:} Benchmarks. Crude language support.

\vspace{1ex}
\noindent\textbf{Year 2:} Benchmarks. Hierarchical aggregation. Compiler optimizations.

\vspace{1ex}
\noindent\textbf{Year 3:} Hierarchical aggregation. SSD-only data structures.

\vspace{1ex}
\noindent\textbf{Year 4:} SSD-only data structures. Detailed system evaluation.
